A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-08-02 ms.tex
Caption

% Shortcuts for this paper
\newcommand{\clustername}{\textsl{NAME}}
\newcommand{\lmcsmc}{LMC--SMC}
\newcommand{\bprp}{\ensuremath{\textrm{BP} - \textrm{RP}}}
\newcommand{\truepm}{\ensuremath{\tilde{\bs{\mu}}}}

@@

\author[0000-0002-1793-3689]{David L. Nidever}
\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717-3840, USA}
\affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719}

@@

\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
The colored lines show $\[\textrm{Fe}/\textrm{H}\] = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.

@@

% Notebook: Proper-motion-membership
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/pm-members-cmd.pdf}
\caption{\todo{APW}
}
\label{fig:pm-members-cmd}
\end{figure}

>>>>

% Shortcuts for this paper
\newcommand{\clustername}{\textsl{NAME}}
\newcommand{\lmcsmc}{LMC--SMC}
\newcommand{\bprp}{\ensuremath{\textrm{BP} - \textrm{RP}}}
\newcommand{\truepm}{\ensuremath{\tilde{\bs{\mu}}}}
\newcommand{\isodist}{\ensuremath{25~\kpc}}

@@

\author[0000-0002-1793-3689]{David L. Nidever}
\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
\affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719}

@@

\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
The colored lines show $\feh = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.
In the next section, we model the distribution of stars in the \decam\ color-magnitude diagram to determine the characteristics of the stellar population.

@@

% Notebook: Proper-motion-membership
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/pm-members-cmd.pdf}
\caption{\gaia\ color-magnitude diagrams for stars in the sky region around \clustername: grey background in both panels shows the distribution for all stars, and black points show stars with $\textrm{probability} > 0.5$ of (kinematically) belonging to \clustername.
Left panel is for stars in the control fields, right panel is for stars in the cluster field.
Colored lines show $\feh = -1$ isochrones from the MIST \citep{TODO} isochrone library for the ages indicated at a distance of \isodist.
}
\label{fig:pm-members-cmd}
\end{figure}
